Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2023-09-25 analysis/paper/London_HauloutBeahvior.Rmd
major updates to most plots, titles, captions
should fully address #50 and also #40. Issue #28 was also addressed by fixing the wx marginal plots to May 15.

theme_set(theme_minimal(base_family = 'Source Sans Pro',
                        base_size = 9))
theme_replace(plot.title.position = "plot")
```

@@

(ref:deployMapCaption) Initial deployment areas for each seal species (bearded, ribbon, and spotted seals) in the study between 2005 and 2020. Regions shown for each species are minimum concave polygons buffered by 60 km for enhanced visibility. The larger region (shaded yellow) indicates the spatial extent of aerial survey effort to date in US waters of the Bering and Chukchi seas. Deployments were initiated across a range of months but only data from 1 March to 15 July were included in the analysis. See Figure \@ref(fig:dataMap) for the spatial distribution of observed data used in the study and Supplemental Materials 1 for additional deployment details.

@@

species_colors <- setNames(met.brewer("Isfahan2",n=3,direction=-1,override.order = TRUE),
                           c("Bearded seal","Ribbon seal","Spotted seal"))
species_labels <- c("Bearded seal" = paste0("<span style = 'color:",
                                            species_colors['Bearded seal'],
                                            ";'>Bearded seal</span>"),
                    "Ribbon seal" = paste0("<span style = 'color:",
                                           species_colors['Ribbon seal'],
                                           ";'>Ribbon seal</span>"),
                    "Spotted seal" = paste0("<span style = 'color:",
                                            species_colors['Spotted seal'],
                                            ";'>Spotted seal</span>")
) %>% as_labeller()

@@

p <- ggplot() +
  layer_spatial(survey_area, color = "#ddc000", 
                fill = "#ddc000", 
                alpha = 0.15,
                linewidth = 0.5) +
  layer_spatial(deploy_sf, aes(fill=species),
                linewidth=0) +
  annotation_spatial(world,
                     linewidth=0,
                     fill = "grey80") +
  geom_sf_text(data = label_coords_bering, aes(label = "Bering sea"), size = 1.75, color = "grey40") +
  geom_sf_text(data = label_coords_chukchi, aes(label = "Chuckchi \nsea"), size = 1.75, color = "grey40") +
  geom_sf_text(data = label_coords_beaufort, aes(label = "Beaufort \nsea"), size = 1.75, color = "grey40") +
  facet_grid(cols = vars(species), labeller = species_labels,
             switch="x") +
  scale_fill_manual(values = met.brewer("Isfahan2",n=3,direction=-1,override.order = TRUE),
                    aesthetics = "fill", 
                    name = "species") + 
  ggtitle("Initial bio-logger deployment locations by species",
          subtitle = 
                 paste0("Bio-loggers were initially deployed on ",
                "<span style = 'color:",species_colors['Bearded seal'],";'>bearded,</span> ", 
                "<span style = 'color:",species_colors['Ribbon seal'],";'>ribbon,</span> ",  
                "and ", 
                "<span style = 'color:",species_colors['Spotted seal'],";'>spotted</span> seals ", 
                "across multiple regions within the Bering, Chukchi, and western Beaufort seas.")) +
  labs(caption = "shaded yellow region indicates spatial extent of aerial survey effort in US waters") +
  theme(legend.position = "none",
        axis.title = element_blank(),
        strip.background = element_blank(),
        strip.placement = "outside",
        strip.text.x = element_markdown(face = "bold"),
        plot.subtitle = element_textbox_simple(margin = ggplot2::margin(b=12)))

@@

```{r examplePlot, include=TRUE, fig.id="examplePlot", fig.cap="Haul-out behavior observations recorded by a bio-logger deployed on a ribbon seal over two years during the months of March, April, and May. This actogram plot represents the transmitted hourly percent-dry values. Areas indicated with an 'X' represent missing data that were not successfully recieved from the tag."}

@@

p <- ggplot(d,aes(day,hour,fill=percent_dry))+
  geom_tile(color= "white",size=0) + 
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "hourly percent dry", aesthetics = "fill",
    guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                           barheight = 0.5, title.hjust = 0.5)
    )

p <- p + facet_grid(year~month, scales = "free_x")
p <- p + scale_x_continuous(breaks = c(5,15,25), expand = c(0,0)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  theme(panel.spacing = unit(0,"line")) +
  ggtitle("Example percent-dry actogram from bio-logger data",
          subtitle = str_wrap("Observation records shown are from a single ribbon seal across a two year deployment. Note that not all records are received from the device.", width = 85)) +
  xlab("day of month") + ylab("hour (UTC)") 
p <- p + 
  geom_point(aes(x = day, y = hour), data = missing_hours, 
             color = "black", shape = 4, size=0.8)
p
```

@@

covariate_tbl %>% 
  select(-Source) %>% 
  flextable() %>% 
  fontsize(size = 9, part = "all") %>% 
  hline(i=8) %>% 
  width(width = 1.0) %>% 
  width(j = ~ Description, width = 2.5)
```

@@

(ref:mapCaption) Spatial distribution of haul-out records during the months of March through July 15 for each of the three species. Data were collated across all years between 2005 and 2020. Each hexagonal cell represents an area of 50 km^2^

@@

ggplot() +
  annotation_spatial(world, 
                     size = 0, 
                     fill = "grey80") +
  layer_spatial(
    data = locs_count, size = 0.125,
    aes(fill = ct)
  ) +
  scale_fill_gradientn(colors = rev(met.brewer("Greek")),
                    trans = "log10", aesthetics = "fill",
    name = "number of locations",
    guide = guide_colorbar(title.position = "bottom", barwidth = 15, 
                           barheight = 0.5, title.hjust = 0.5)) + 
  facet_grid(~ species) +
  theme(legend.position = "bottom") +
  ggtitle("Spatial distribution of haul-out behavior records") +
  labs(caption = bquote("One hexagonal cell represents 50"~km^2))
```

@@

ggplot(data = seal_hours_tbl, aes(x = yday, y = n, fill = n))+
  geom_col() +
        scale_fill_gradientn(colors = rev(met.brewer("Greek"))) +
        scale_x_continuous(breaks = c(60, 91, 121, 152, 182),
                           labels = c("01 March", "01 April", "01 May", "01 June", "01 July"),
                           expand = expansion(mult = c(0, 0))) +
        scale_y_continuous(expand = expansion(mult = c(0, 0))) +
  guides(fill = guide_colorbar(title.position = "bottom", 
                               title.hjust = 0.5, barwidth = 15,
                               barheight = 0.5)) +
  facet_grid(species ~ .) + 
  theme(axis.text.x = element_text(hjust = 0),
        axis.text.y = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom") +
  labs(fill = "seal-hours of bio-logger data") +
  ggtitle("Density of haul-out behavior observations by species",
          subtitle = str_wrap("data are grouped by day-of-year and presented in seal-hours collated across years (2005-2020) from March through July"))

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill = ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Bearded seals rest on sea ice around solar noon and solar midnight")
p
```

@@

```{r beardedHOwx, fig.asp = 1, include=TRUE, fig.cap="Marginal effects of temperature, wind, pressure, and precipitation on the predicted haul-out probability of bearded seals combined across all age and sex classifications. Hour of the day was fixed at local solar noon and day-of-year held at the day of peak haul-out for bearded seals. Vertical lines represent the 95\\% confidence interval around the predicted haul-out probability."}

@@

```{r ribbonHOCal, fig.asp = 0.9, include=TRUE, fig.cap="Predicted hourly haul-out probability of ribbon seals from 1 March to 15 July for each age and sex class used in the model. Adult females are indicated by 'ADULT.F' and 'ADULT.M' indicates adult males. 'SUBADULT' and 'YOUNG OF YEAR' age classes include both sexes. Hour of the day was fixed at local solar noon."}

@@

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob)) +
  geom_tile(color = "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour = "white")) +
  theme(axis.ticks = element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Ribbon seals rest on sea ice in late spring and around solar noon.")
p
```

@@

```{r ribbonHOwx, fig.asp = 0.9, include=TRUE, fig.cap="Marginal effects of temperature, wind, pressure, and precipitation on the predicted haul-out probability of ribbon seals within each age and sex classification. Hour of the day was fixed at local solar noon and day-of-year held at the average day of peak haul-out for ribbon seals. Vertical lines represent the 95\\% confidence interval around the predicted haul-out probability."}

@@

```{r spottedHOCal, fig.asp = 0.9, include=TRUE, fig.cap="Predicted hourly haul-out probability of spotted seals from 1 March to 15 July for each age and sex class used in the model. Adult females are indicated by 'ADULT.F' and 'ADULT.M' indicates adult males. 'SUBADULT' and 'YOUNG OF YEAR' age classes include both sexes. Hour of the day was fixed at local solar noon."}

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill=ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Spotted seals rest on sea ice in late spring and around solar noon.")
p
```

@@

```{r spottedHOwx,fig.asp = 0.9, include=TRUE, fig.cap="Marginal effects of temperature, wind, pressure, and precipitation on the predicted haul-out probability of spotted seals within each age and sex classification. Hour of the day was fixed at local solar noon and day-of-year held at the average day of peak haul-out for spotted seals. Vertical lines represent the 95\\% confidence interval around the predicted haul-out probability."}

@@

pal <- c(RColorBrewer::brewer.pal(12, "Paired"), "black")

p <- ggplot(plot_df %>% filter(age_sex != "YOUNG OF YEAR"), aes(yday, ho_prob)) +
  geom_pointrange(aes(ymin = lower95, ymax = upper95), alpha = 0.25, 
                  stroke = 0, color = "grey80") +
  geom_pointrange(data = peak_ho_df,
                  mapping = aes(yday, ho_prob, ymin = 0, ymax = ho_prob, color = year),
                  shape = 15) +
  scale_color_discrete(type = pal) +
  scale_x_continuous(breaks = c(74,105,135,166),
                     labels = c("15-Mar", "15-Apr", "15-May", "15-Jun")) +
  facet_grid(age_sex~species) +
  theme(legend.position = "bottom") +
  xlab("") + ylab("haul-out probability") +
  ggtitle("Annual variability in the timing of peak haul-out probability")
 p
```

>>>>

theme_set(theme_minimal(base_family = 'Spline Sans',
                        base_size = 9))
theme_update(
  plot.title.position = "plot",
  # left-align title
  plot.caption.position = "plot",
  # right-align caption
  plot.title = element_text(face = "bold"),
  # larger, bold title
  plot.subtitle = element_textbox_simple(
    color = "grey30",
    margin = ggplot2::margin(t = 0, b = 12, r = 60)
  ),
  plot.caption = element_text(color = "grey30"),
  # change color of caption
  panel.grid.minor = element_blank() # no minor grid lines
)

# use a named vector for explicit matching
species_colors <- c(
  'Spotted seal' = "#52BCA3",
  'Bearded seal' = "#E58606",
  'Ribbon seal' = "#5D69B1"
)

age_sex_labels <- c(
  "ADULT.F" = "adult female",
  "ADULT.M" = "adult male",
  "SUBADULT" = "subadult",
  "YOUNG OF YEAR" = "young of year",
  "ALL AGES" = "all ages"
)

@@

(ref:deployMapCaption) Initial deployment areas for each seal species (bearded, ribbon, and spotted seals) in the study between 2005 and 2020. Solid regions shown for each species are minimum concave polygons buffered by 60 km for enhanced visibility. The larger, shaded region indicates the spatial extent of aerial survey effort to date in US waters of the Bering and Chukchi seas. Deployments were initiated across a range of months but only data from 1 March to 15 July were included in the analysis. See Figure \@ref(fig:dataMap) for the spatial distribution of observed data used in the study and Supplemental Materials 1 for additional deployment details.

@@

species_labels <- c("Bearded seal" = paste0("<span style = 'color:",
                                            species_colors['Bearded seal'],
                                            ";'>Bearded seal</span>"),
                    "Ribbon seal" = paste0("<span style = 'color:",
                                           species_colors['Ribbon seal'],
                                           ";'>Ribbon seal</span>"),
                    "Spotted seal" = paste0("<span style = 'color:",
                                            species_colors['Spotted seal'],
                                            ";'>Spotted seal</span>")
) %>% as_labeller()

@@

p <- ggplot() +
  layer_spatial(survey_area, color = "#A26E7C", 
                fill = "#A26E7C", 
                alpha = 0.15,
                linewidth = 0.5) +
  layer_spatial(deploy_sf, aes(fill=species),
                linewidth=0) +
  annotation_spatial(world,
                     linewidth=0,
                     fill = "grey80") +
  geom_sf_text(data = label_coords_bering, aes(label = "Bering sea"), size = 1.65, color = "grey30") +
  geom_sf_text(data = label_coords_chukchi, 
               aes(label = "Chuckchi \nsea"), size = 1.65, lineheight = .85, color = "grey30") +
  geom_sf_text(data = label_coords_beaufort, 
               aes(label = "Beaufort \nsea"), size = 1.65, lineheight = .85, color = "grey30") +
  facet_grid(cols = vars(species), labeller = species_labels,
             switch="x") +
  scale_fill_manual(values = species_colors,
                    aesthetics = "fill", 
                    name = "species") + 
  labs(title = "Initial bio-logger deployment locations by species",
          subtitle = 
                 paste0("Bio-loggers were initially deployed on ",
                "<span style = 'color:",species_colors['Bearded seal'],";'>bearded,</span> ", 
                "<span style = 'color:",species_colors['Ribbon seal'],";'>ribbon,</span> ",  
                "and ", 
                "<span style = 'color:",species_colors['Spotted seal'],";'>spotted</span> seals ", 
                "across multiple regions within the Bering, Chukchi, and western Beaufort seas."),
       caption = "outlined region indicates spatial extent of aerial survey effort in US waters") +
  theme(legend.position = "none",
        axis.title = element_blank(),
        strip.background = element_blank(),
        strip.placement = "outside",
        strip.text.x = element_markdown(face = "bold"),
        plot.caption = element_markdown(color = "#A26E7C")
  )

@@

```{r examplePlot, include=TRUE, fig.id="examplePlot", fig.cap="Haul-out behavior observations recorded by a bio-logger deployed on a ribbon seal over two years during the months of March, April, and May. This actogram plot represents the transmitted hourly percent-dry values. Not all data during a deployment are reliably transmitted from the bio-logger and since data are transmitted in 24-hour chunks occasional missing days are present in the record. Here, missing data that were not successfully recieved from the device are represented as empty rectangles."}

@@

p <- ggplot(d,aes(day,hour,fill=percent_dry))+
  geom_tile(linewidth = 0.1, color = "grey75") + 
  scico::scale_fill_scico(palette = "nuuk", direction = 1,
                       name = "hourly percent dry", aesthetics = "fill",
    guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                           barheight = 0.5, title.hjust = 0.5)
    ) +
  geom_tile(data = missing_hours, fill = NA, color = "grey30", linewidth = 0.2) +
  coord_cartesian(clip = "off")

label_df <- data.frame(year = 2016, month = "Apr",day = 1, hour = 12,
                       percent_dry = 0,
                       lab = "**Missing Data**<br>not all data are reliably received from the bio-logger") |> 
  mutate(month = forcats::fct_relevel(month,c("Mar","Apr","May","Jun")))

curve_df <- data.frame(year = 2016, 
                       month = "Apr", 
                       day = 1, day_end = 2, 
                       hour = 8, hour_end = 0,
                       percent_dry = 0) |> 
  mutate(month = forcats::fct_relevel(month,c("Mar","Apr","May","Jun")))

p <- p +
  geom_textbox(
    data = label_df,
    mapping = aes(day, hour, label = lab),
    width = grid::unit(0.65, "npc"), # 65% of plot panel width
    halign = 0, valign = 0.5,
    nudge_y = 2,
    size = 2.75, box.size = NA,
    lineheight = .9,
    fill = NA, 
    label.color = NA,
  ) +
  geom_curve(
    data = curve_df,
    mapping = aes(x = day, y = hour, xend = day_end, yend = hour_end),
    curvature = 0
  )

p <- p + facet_grid(year~month, scales = "free_x")
p <- p + scale_x_continuous(breaks = c(5,15,25), expand = c(0,0)) +
  scale_y_continuous(breaks = c(4,12,20), labels = c("04:00","12:00","20:00"))

p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  theme(panel.spacing = unit(0,"line")) +
  ggtitle("Example percent-dry actogram from bio-logger data",
          subtitle = "Observation records shown are from a single ribbon seal across a two year deployment.") +
  xlab("day of month") + ylab("hour (UTC)")

@@

covariate_tbl %>% 
  flextable() %>% 
  fontsize(size = 9, part = "all") %>% 
  hline(i=8) %>% 
  width(width = 1.0) %>% 
  width(j = ~ Description, width = 2.5)
```

@@

(ref:mapCaption) Spatial distribution of haul-out records during the months of March through July 15 for each of the three species. Linking location estimates with haul-out records in space and time allows for inclusion of weather covariates in the final model. For this visualization, data were collated across all years between 2005 and 2020 and each hexagonal cell represents an area of 50 km^2^

@@

ggplot() +
  annotation_spatial(world,
                     linewidth = 0,
                     fill = "grey80") +
  layer_spatial(
    data = locs_count,
    aes(fill = ct),
    linewidth = 0.1,
    color = "grey75"
  ) +
  scico::scale_fill_scico(
    palette = "imola",
    trans = "log10",
    aesthetics = "fill",
    name = "number of locations",
    guide = guide_colorbar(
      title.position = "bottom",
      barwidth = 15,
      barheight = 0.5,
      title.hjust = 0.5
    )
  ) +
  facet_grid( ~ species) +
  labs(
    title = "Spatial distribution of haul-out behavior records",
    subtitle = "Location estimates were linked by time with haul-out records. 
    Data are shown collated across 2005-2020 between 01 March-15 July
    for each of the three species.",
    caption = bquote("One hexagonal cell represents 50" ~ km ^ 2)
  ) +
  theme(
    legend.position = "bottom"
  )
```

@@

ggplot(data = seal_hours_tbl, aes(x = yday, y = n, fill = n))+
  geom_col() +
        scico::scale_fill_scico(palette = "oslo", direction = -1) +
        scale_x_continuous(breaks = c(60, 91, 121, 152, 182),
                           labels = c("01 March", "01 April", "01 May", "01 June", "01 July"),
                           expand = expansion(mult = c(0, 0))) +
        scale_y_continuous(expand = expansion(mult = c(0, 0))) +
  guides(fill = guide_colorbar(title.position = "bottom", 
                               title.hjust = 0.5, barwidth = 15,
                               barheight = 0.5)) +
  facet_grid(species ~ .) + 
  labs(fill = "seal-hours of bio-logger data",
       title = "Seasonal density of haul-out behavior observations by species",
       subtitle = "Data are grouped by day-of-year and presented in seal-hours collated across 
       years (2005-2020) from March through July.") +
  theme(axis.text.x = element_text(hjust = 0),
        axis.text.y = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        plot.subtitle = element_textbox_simple(
          color = "grey30",
          margin = ggplot2::margin(t = 0, b = 0, r = 60)
        )
  )

@@

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob, color = ho_prob)) +
  geom_tile(linewidth = 0.15) +
  scico::scale_fill_scico(palette = "navia", direction = 1,
                          begin = 0.1, end = 1,
                       name = "haul-out probability", 
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  ) +
  scico::scale_color_scico(palette = "navia", direction = 1,
                           begin = 0.1, end = 1,
                           limits = c(0,1)) +
  guides(col = FALSE)

p <- p + facet_grid(age_sex~month,
                    labeller = labeller(
                      age_sex = age_sex_labels
                    ))
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20), labels = c("04","12", "20"))
p <- p + theme(legend.position = "bottom",
               strip.background = element_rect(colour="white"),
               axis.ticks=element_blank()) + 
  xlab("day of month") + ylab("local solar hour") +
  labs(title = "Bearded seal predicted haul-out probability",
       subtitle = "Our model predicts lower haul-out probability for bearded seals overall 
       compared to ribbon and spotted seals. Highest probability is associated with solar noon and midnight.")
p
```

@@

```{r beardedHOwx, fig.asp = 1, include=TRUE, fig.cap="Marginal effects of temperature, wind, pressure, and precipitation on the predicted haul-out probability of bearded seals combined across all age and sex classifications. Hour of the day was fixed at local solar noon and day-of-year fixed at 15 May. Vertical lines represent the 95\\% confidence interval around the predicted haul-out probability."}

@@

```{r ribbonHOCal, fig.asp = 0.9, include=TRUE, fig.cap="Predicted hourly haul-out probability of ribbon seals from 1 March to 15 July for each age and sex class used in the model. There is an apparent seasonal progression with subadults hauling out earlier in the season followed by adult males and, then, adult females. Predictions for young of the year show their transition from newly weaned pups resting on the ice to more in-water activities."}

@@

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob, color = ho_prob)) +
  geom_tile(linewidth = 0.15) +
  scico::scale_fill_scico(palette = "navia", direction = 1,
                          begin = 0.1, end = 1,
                       name = "haul-out probability", 
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  ) +
  scico::scale_color_scico(palette = "navia", direction = 1,
                           begin = 0.1, end = 1,
                           limits = c(0,1)) +
  guides(col = FALSE)

p <- p + facet_grid(age_sex~month,
                    labeller = labeller(
                      age_sex = age_sex_labels
                    ))
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20), labels = c("04","12", "20"))
p <- p + theme(legend.position = "bottom",
               strip.background = element_rect(colour = "white"),
               axis.ticks = element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Ribbon seal predicted haul-out probability.",
          subtitle = "Our model predicts increased haul-out probability 
          for ribbon seals centered on solar noon and a sequential 
          seasonal pattern linked to age and sex classifications.")
p
```

@@

```{r ribbonHOwx, fig.asp = 0.9, include=TRUE, fig.cap="Marginal effects of temperature, wind, pressure, and precipitation on the predicted haul-out probability of ribbon seals within each age and sex classification. Hour of the day was fixed at local solar noon and day-of-year fixed at 15 May. Vertical lines represent the 95\\% confidence interval around the predicted haul-out probability."}

@@

```{r spottedHOCal, fig.asp = 0.9, include=TRUE, fig.cap="Predicted hourly haul-out probability of spotted seals from 1 March to 15 July for each age and sex class used in the model. Compared to ribbon seals, the period of increased haul-out behavior is broader and there is more alignment in the seasonal timing of haul-out behavior across age and sex classifications. This likely reflects the triad behavior in spotted seals when suitor males haul out with nursing females. As with ribbon seals, redictions for young of the year show their transition from newly weaned pups resting on the ice to more in-water activities."}

@@

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob, color = ho_prob)) +
  geom_tile(linewidth = 0.15) +
  scico::scale_fill_scico(palette = "navia", direction = 1,
                          begin = 0.1, end = 1,
                       name = "haul-out probability", 
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  ) +
  scico::scale_color_scico(palette = "navia", direction = 1,
                           begin = 0.1, end = 1,
                           limits = c(0,1)) +
  guides(col = FALSE)

p <- p + facet_grid(age_sex~month,
                    labeller = labeller(
                      age_sex = age_sex_labels
                    ))
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20), labels = c("04","12", "20"))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Spotted seal predicted haul-out probability.",
          subtitle = "Our model predicts increased haul-out probability 
          for spotted seals centered on solar noon with general alignment in the
          seasonal timing across age and sex classifications.")
p
```

@@

```{r spottedHOwx,fig.asp = 0.9, include=TRUE, fig.cap="Marginal effects of temperature, wind, pressure, and precipitation on the predicted haul-out probability of spotted seals within each age and sex classification. Hour of the day was fixed at local solar noon and day-of-year fixed at 15 May. Vertical lines represent the 95\\% confidence interval around the predicted haul-out probability."}

@@

pal <- c(rcartocolor::carto_pal(12,'Bold')[1:11],
         rcartocolor::carto_pal(12,'Antique')[1:11])

p <-
  ggplot(plot_df %>% filter(age_sex != "YOUNG OF YEAR"), aes(yday, ho_prob)) +
  geom_pointrange(
    aes(ymin = lower95, ymax = upper95),
    alpha = 0.25,
    stroke = 0,
    color = "grey80"
  ) +
  geom_pointrange(
    data = peak_ho_df,
    mapping = aes(
      yday,
      ho_prob,
      ymin = 0,
      ymax = ho_prob,
      color = year
    ),
    shape = 15
  ) +
  scale_color_discrete(type = pal) +
  scale_x_continuous(
    breaks = c(74, 105, 135, 166),
    labels = c("15-Mar", "15-Apr", "15-May", "15-Jun")
  ) +
  facet_grid(age_sex ~ species) +
  ylab("haul-out probability") +
  labs(title = "Annual variability in the timing of peak haul-out probability",
       subtitle = "Predictions for ribbon and spotted seals are shown for local 
       solar noon and under smoothed weather conditions") +
  theme(legend.position = "bottom",
        axis.title.x = element_blank())
